Racets: Policy{-}Agnostic Programming in Racket

### 2018-07-23 paper/paper.tex
various tweaks to bib and adding a tiny bit of impl sec

>>>>

We have implemented Racets as a set of Racket macros which can be
employed as a language using Racket's \texttt{\#lang reader}
facility. So far, we have included macros for many of Racket's core
forms including application, \code{if}, \code{lambda}, and
references. We leave others (including continuation marks) to future
work. Additionally, Racets does not support first-class control. There
has been recent work in handling exceptions in the context of faceted
execution~\cite{Austin:17}, however reconciling first-class control in
general remains (to our knowledge) an open problem.

Because of Racket's flexible macro system, our implementation of
faceted execution is much smaller than other systems: our core macros
comprise only 170 source lines of Racket, with another 120 lines of
library code to perform various facet-related functions.

We plan to make our prototype of Racets available publicly.
